---
title: "Simple document"
output: github_document
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
```

## Import some data

I want to import `FAS_litters.csv`. 

Relative paths = giving directions from where I am now to where I want to be 
  As long as I'm sharing this whole folder, I can send this to anyone 
Absolute paths = absolute directions from the beginning of your computer 

```{r}
liters_df = read_csv("data/FAS_litters.csv")
```
This imported the dataset into R. 
This assigned litters_df as the name of that data into the R. 

Now I want better names 
- backticks around litter number, etc. --> you can't have a variable name with spaces in it 

```{r}
names(liters_df)

liters_df = janitor::clean_names(liters_df)

names(liters_df)
```

1) shows names in data frame
2) liters_df replaces the old data frame with the cleaned one & then cleans names of variables (this is in the janitor package --> since we only need the clean names function, we only call that function since the janitor package is really big)
3) tests to make sure it works! 

```{r}
liters_df

head(liters_df)
tail(liters_df)
```

This is showing me the variable names, the 10 first rows, and how many additional rows there are 
Second row is also telling us the types of variables (character vs. double)

Prints out the top and bottom to make sure the beginning and end are "normal" 

```{r, eval=FALSE}
view(liters_df)
```

Use this to view all the data (in an excel within R)

eval = FALSE --> This is interactive, but can mess up the rmarkdown, so make sure it doesn't show it in the Knitted doc 

```{r}
skimr::skim(liters_df)
```
Shows a little information about everything

